---
title: "N-mixture models in NIMBLE"
description: |
  Simulations investigating use of N-mixture models for NABat data
output:
  distill::distill_article:
    self_contained: false
    toc: true
    toc_depth: 3
bibliography: bibliography.bib
csl: biometrics_notes.csl
---

```{r setup, include = F}
rm(list = ls())

library(knitr)
hook_chunk <- knitr::knit_hooks$get('chunk')
knit_hooks$set(chunk = function(x, options) {

  # add latex commands if chunk option singlespacing is TRUE
  if(isTRUE(options$singlespacing)){
    return(sprintf("\\singlespacing\n %s \n\\doublespacing", hook_chunk(x, options)))
  } else{
    return(hook_chunk(x, options))
  }
})
knitr::opts_chunk$set(
  fig.align = "center",
  tidy = T,
  singlespacing = TRUE,
  cache = TRUE,
  fig.dim = c(10,8),
  message = FALSE,
  warning = FALSE,
  comment = NA,
  echo = F
)

# packages
packs <- c("tidyverse", "rstan", "sf", "coda", "proxy", "daymetr", "prism", "stars", "raster", "exactextractr", "lubridate", "ggnewscale", "loo", "nimble")
sapply(packs, require, character.only = T)
rm(packs)
options(tidyverse.quiet = TRUE)

# convenience
`%notin%` <- Negate("%in%")

# stan settings
options(mc.cores = parallel::detectCores() - 1)
rstan_options(auto_write = TRUE)

# data files from manuscript simulations
sim1_dfs <- readRDS("data/sim1_dfs.rds")

# functions
nimble_summary <- function(fit, warmup = nrow(fit[[1]])/2, thin = 1){
  # convert to coda for normal summary
  fit_warmup <- lapply(fit, function(x) x[(warmup+1):nrow(x),])
  coda_samples <- coda::as.mcmc.list(lapply(fit_warmup, function(x) as.mcmc(
    x, start = warmup+1, end = nrow(fit), thin = thin
  )))
  
  sum <- summary(coda_samples)
  params <- dimnames(sum$statistics)[[1]]
  tmp_sum <- cbind(sum$statistics, sum$quantiles)
  
  # get r hat / n_eff
  mat <- matrix(NA, nrow = nrow(tmp_sum), ncol = 3)
  colnames(mat) <- c("Rhat", "ess_bulk", "ess_tail")
  for(i in 1:nrow(tmp_sum)){
    tmp <- sapply(fit, function(x) x[,i])
    mat[i,] <- c(Rhat(tmp), ess_bulk(tmp), ess_tail(tmp))
  }
  
  # out 
  out <- cbind(tmp_sum, mat)
  return(out)
}
trace_plot <- function(samples, which = c("sigma"), nrow = 1){
  niter <- dim(samples[[1]])[1]
  nchains <- length(samples)
  params <- colnames(samples[[1]])
  nrow_ <- nrow
  
  combined_samples <- do.call("rbind", samples)
  combined_samples <- combined_samples %>%
    as_tibble %>%
    mutate(iter = rep(1:niter, nchains), chain = factor(rep(1:nchains, each = niter))) %>%
    dplyr::select(chain, iter, everything()) %>%
    pivot_longer(cols = -c(1:2), names_to = "param", values_to = "trace")
  
  if(all(is.numeric(which))) which <- unique(combined_samples$param)[which]
  
  p <- combined_samples %>%
    filter(param %in% which) %>%
    ggplot() + 
    geom_line(aes(x = iter, y = trace, col = chain, group = chain)) +
    theme_bw() +
    facet_wrap(~ param, scales = "free_y", nrow = nrow_)
  
  return(p)
  
}
```

# Introduction

The purpose of this document is to showcase how N-mixture models [@royle2004] may be used with the NABat data pipeline to model colony counts and capture records. 

# Model description

## N-mixture model

The following is a condensed description of the model discussed by @royle2004. Let $N_i$ denote the number of individuals _available for capture_ at site $i$ and $p_{ij}$ denote the probability of detecting an individual on visit $j$ to site $i$. Then,
\[
\begin{split}
N_i &\sim \text{Poisson}(\lambda_i) \\
y_{ij} &\sim \text{Binomial}(N_i, p_{ij})
\end{split}
\]
Alternatively, a negative binomial sampling model can be placed on the the latent number of individuals available for capture. 
\[
\begin{split}
N_i &\sim \text{Negative binomial}(\mu_i, \phi) \\
y_{ij} &\sim \text{Binomial}(N_i, p_{ij})
\end{split}
\]

## Zero-inflated N-mixture model

In some cases, some sites may not be tenable for the target species. To account for the extra zeros induced by habitat insuitability, an occupancy layer can be added, resulting in a zero-inflated N-mixture model. 
\[
\begin{split}
Z_i &\sim \text{Bernoulli}(\psi_i) \\
N_i | z_i&\sim \text{Negative binomial}(z_i * \mu_i, \phi) \\
y_{ij} | N_i &\sim \text{Binomial}(N_i, p_{ij})
\end{split}
\]

# Simulated experiments

```{r}
# seed = 1
# dat <- sim1_dfs$mt_covs_grid
# visit_dat <- sim1_dfs$visit_covs
# beta = rnorm(2)
# alpha = rnorm(2)
# delta = rnorm(2)
# phi = abs(rnorm(1))
# family = "negbin"
# zif = TRUE
# nsites = 75
# nvisits = 8
nmixture_sim <- function(seed = 1, dat, visit_dat, family = "negbin", zif = TRUE, nsites = 75, nvisits = 8, beta = rnorm(2), alpha = rnorm(2), delta = rnorm(2), phi = abs(rnorm(1))){
  # set seed
  set.seed(seed)
  
  # couple checks 
  if(length(beta) > 8) stop("Only 8 covariates for Z are supported")
  if(length(alpha) > 8) stop("Only 8 covariates for N are supported")
  if(length(delta) > 6) stop("Only 6 covariates for y are supported")
  
  # occupancy first 
  out <- dat %>% mutate(ndx = 1:n())
  if(zif){
    p_beta <- length(beta)
    X <- dat %>%
      as_tibble %>%
      dplyr::select(mean_temp, precip, DEM_max, p_forest, dist_mines, physio_div, p_wetland) %>%
      mutate_at(vars(mean_temp:p_wetland), ~c(scale(.x))) %>%
      dplyr::select(1:(p_beta-1)) %>%
      model.matrix(~., .)
    out$xb <- c(X %*% beta)
    out$psi <- with(out, exp(xb) / (1+exp(xb)))
    out$z <- rbinom(nrow(out), 1, out$psi)
  }
  
  # simulate counts first
  if(zif){
    if(family == "negbin"){
      p_alpha <- length(alpha)
      W <- dat %>%
        as_tibble %>%
        dplyr::select(mean_temp, precip, DEM_max, p_forest, dist_mines, physio_div, p_wetland) %>%
        mutate_at(vars(mean_temp:p_wetland), ~c(scale(.x))) %>%
        dplyr::select(1:(p_alpha-1)) %>%
        model.matrix(~., .)
      out$wa <- c(W %*% alpha)
      out$N <- rnbinom(nrow(out), mu = out$z * exp(out$wa), size = phi)
    } else{
      p_alpha <- length(alpha)
      W <- dat %>%
        as_tibble %>%
        dplyr::select(mean_temp, precip, DEM_max, p_forest, dist_mines, physio_div, p_wetland) %>%
        mutate_at(vars(mean_temp:p_wetland), ~c(scale(.x))) %>%
        dplyr::select(1:(p_alpha-1)) %>%
        model.matrix(~., .)
      out$wa <- c(W %*% alpha)
      out$N <- rpois(nrow(out), out$z * exp(out$wa))
    }
  } else{
    if(family == "negbin"){
      p_alpha <- length(alpha)
      W <- dat %>%
        as_tibble %>%
        dplyr::select(mean_temp, precip, DEM_max, p_forest, dist_mines, physio_div, p_wetland) %>%
        mutate_at(vars(mean_temp:p_wetland), ~c(scale(.x))) %>%
        dplyr::select(1:(p_alpha-1)) %>%
        model.matrix(~., .)
      out$wa <- c(W %*% alpha)
      out$N <- rnbinom(nrow(out), mu = exp(out$wa), size = phi)
    } else{
      p_alpha <- length(alpha)
      W <- dat %>%
        as_tibble %>%
        dplyr::select(mean_temp, precip, DEM_max, p_forest, dist_mines, physio_div, p_wetland) %>%
        mutate_at(vars(mean_temp:p_wetland), ~c(scale(.x))) %>%
        dplyr::select(1:(p_alpha-1)) %>%
        model.matrix(~., .)
      out$wa <- c(W %*% alpha)
      out$N <- rpois(nrow(out), exp(out$wa))
    }
  }
  
  # detections
  out2 <- visit_dat %>%
    left_join(
      ., 
      out %>% dplyr::select(grts_id, N),
      by = "grts_id"
    ) %>%
    mutate(ndx = 1:n())
  p_delta <- length(delta)
  V <- out2 %>%
    as_tibble %>%
    dplyr::select(tmean, ppt, tdmean, vpdmax, lunar_illum) %>%
    mutate_at(vars(tmean:lunar_illum), ~c(scale(.x))) %>%
    dplyr::select(1:(p_delta-1)) %>%
    model.matrix(~., .)
  out2$vd <- c(V %*% delta)
  out2$p <- with(out2, exp(vd) / (1+exp(vd)))
  out2$y <- rbinom(nrow(out2), size = out2$N, out2$p)
  
  # subset
  site_df_obs <- out %>%
    sample_n(nsites) %>% arrange(ndx) %>%
    dplyr::select(ndx, everything())
  visit_df_obs <- out2 %>%
    filter(grts_id %in% site_df_obs$grts_id) %>%
    group_by(grts_id) %>%
    sample_n(nvisits) %>%
    ungroup %>%
    arrange(ndx)
  
  
  # save
  if(zif){
    out3 <- list(
      full_design = list(
        X = X,
        W = W,
        V = V
      ),
      obs_design = list(
        X = X[site_df_obs$ndx,],
        W = W[site_df_obs$ndx,],
        V = V[visit_df_obs$ndx,]
      ),
      site_df = out,
      visit_df = out2,
      site_df_obs = site_df_obs,
      visit_df_obs = visit_df_obs,
      params = list(
        beta = beta, alpha = alpha, delta = delta, phi = phi
      )
    )
  } else{
    out3 <- list(
      full_design = list(
        W = W,
        V = V
      ),
      obs_design = list(
        W = W[site_df_obs$ndx,],
        V = V[visit_df_obs$ndx,]
      ),
      site_df = out,
      visit_df = out2,
      site_df_obs = site_df_obs,
      visit_df_obs = visit_df_obs,
      params = list(
        beta = beta, alpha = alpha, delta = delta, phi = phi
      )
    )
  }
  
  return(out3)
}
```

## Poisson N-mixture model

```{r, eval = T, cache = F}
pois_code <- nimbleCode({
  # likelihood
  for(site in 1:nsites){
    log(lambda[site]) <- inprod(alpha[1:p_alpha], W[site, 1:p_alpha])
    N[site] ~ dpois(lambda = lambda[site])
  }
  for(row in 1:nrows){
    logit(p[row]) <- inprod(delta[1:p_delta], V[row, 1:p_delta])
    y[row] ~ dbinom(prob = p[row], size = N[site_ndx[row]])
  }

  # priors
  for(i in 1:p_alpha){
    alpha[i] ~ dnorm(0, sd = 2)
  }
  for(i in 1:p_delta){
    delta[i] ~ dnorm(0, sd = 2)
  }
})
pois_code
```

### Simulated data

```{r, eval = T, cache = F}
# simulate data
dat <- nmixture_sim(
  seed = 01242023,
  dat = sim1_dfs$mt_covs_grid,
  visit_dat = sim1_dfs$visit_covs,
  family = "poisson",
  zif = FALSE,
  nsites = 75, 
  nvisits = 8
)
```

```{r}
ggplot() +
  geom_sf(
    data = dat$site_df, size = .1, fill = NA
  ) +
  geom_sf(
    data = dat$site_df_obs, size = .1, aes(fill = log(N), col = log(N))
  ) +
  scale_color_gradientn(
    colors = c("#a1d76a", "#e9a3c9") # PiYG palette
  ) + 
  scale_fill_gradientn(
    colors = c("#a1d76a", "#e9a3c9") # PiYG palette
  ) +
  theme_bw()
```

### Fit model

```{r, eval = F}
# fit model
fit <- nimbleMCMC(
  code = pois_code,
  data = list(
    y = dat$visit_df_obs$y
  ),
  constants = list(
    nsites = nrow(dat$site_df_obs),
    nrows = nrow(dat$visit_df_obs),
    W = dat$obs_design$W,
    V = dat$obs_design$V,
    p_alpha = length(dat$params$alpha),
    p_delta = length(dat$params$delta),
    site_ndx = dat$visit_df_obs$grts_id %>% 
      as.factor %>% as.numeric
  ),
  monitors = c("alpha", "delta", "N", "p"),
  niter = 10000,
  nburnin = 500,
  nchains = 3
)
saveRDS(fit, file = "fits/pois.rds")
```

### Diagnostics

```{r}
fit <- readRDS("fits/pois.rds")
trace_plot(fit, c("alpha[1]", "alpha[2]", "delta[1]", "delta[2]"), nrow = 2)
```

### Posterior summaries

```{r}
tmp <- nimble_summary(fit)
tbl1 <- tibble(
  param = rownames(tmp),
  mean = tmp[,1],
  lwr = tmp[,5],
  upr = tmp[,9],
  rhat = tmp[,10],
  neff_bulk = tmp[,11],
  neff_tail = tmp[,12]
) %>%
  mutate(
    truth = c(
      dat$site_df_obs$N,
      dat$params$alpha, dat$params$delta,
      dat$visit_df_obs$p
    )
  ) %>%
  mutate(
    capture = factor(
      ifelse(truth >= lwr & truth <= upr, 1, 0)
    )
  ) %>%
  mutate(
    mean_centered = mean-truth,
    lwr_centered = lwr-truth,
    upr_centered = upr-truth
  )

tbl1 %>%
  filter(grepl("alpha", param) | grepl("delta", param)) %>%
  ggplot() +
  geom_pointrange(
    aes(y = param, xmin = lwr_centered, xmax = upr_centered, x = mean_centered, col = capture)
  ) +
  theme_bw() +
  geom_vline(aes(xintercept = 0))

tbl1 %>%
  filter(grepl("N", param)) %>%
  sample_n(15) %>%
  ggplot() +
  geom_pointrange(
    aes(y = param, xmin = lwr_centered, xmax = upr_centered, x = mean_centered, col = capture)
  ) +
  theme_bw() +
  geom_vline(aes(xintercept = 0))

tbl1 %>%
  filter(grepl("p", param)) %>%
  sample_n(20) %>%
  ggplot() +
  geom_pointrange(
    aes(y = param, xmin = lwr_centered, xmax = upr_centered, x = mean_centered, col = capture)
  ) +
  theme_bw() +
  geom_vline(aes(xintercept = 0))
```

### Baby simulation study

Twenty simulated data sets with random generating values. 

```{r, eval = F}
run_sims <- function(nsims){
  out <- list()
  
  pb <- txtProgressBar(min = 0, max = nsims, style = 3, width = 50, char = "=")  
  for(sim in 1:nsims){
    sim_ <- sim
    
    # simulate data
    dat <- nmixture_sim(
      seed = sim,
      dat = sim1_dfs$mt_covs_grid,
      visit_dat = sim1_dfs$visit_covs,
      family = "poisson",
      zif = FALSE,
      nsites = 75, 
      nvisits = 8
    )
    
    # fit model
    fit <- suppressMessages({nimbleMCMC(
      code = pois_code,
      data = list(
        y = dat$visit_df_obs$y
      ),
      constants = list(
        nsites = nrow(dat$site_df_obs),
        nrows = nrow(dat$visit_df_obs),
        W = dat$obs_design$W,
        V = dat$obs_design$V,
        p_alpha = length(dat$params$alpha),
        p_delta = length(dat$params$delta),
        site_ndx = dat$visit_df_obs$grts_id %>% 
          as.factor %>% as.numeric
      ),
      monitors = c("alpha", "delta", "N", "p"),
      niter = 10000,
      nburnin = 500,
      nchains = 3,
      progressBar = F
    )})
    
    # summarize
    tmp <- nimble_summary(fit)
    tbl1 <- tibble(
      param = rownames(tmp),
      mean = tmp[,1],
      lwr = tmp[,5],
      upr = tmp[,9],
      rhat = tmp[,10],
      neff_bulk = tmp[,11],
      neff_tail = tmp[,12]
    ) %>%
      mutate(
        truth = c(
          dat$site_df_obs$N,
          dat$params$alpha, dat$params$delta,
          dat$visit_df_obs$p
        )
      ) %>%
      mutate(
        capture = factor(
          ifelse(truth >= lwr & truth <= upr, 1, 0)
        )
      ) %>%
      mutate(
        mean_centered = mean-truth,
        lwr_centered = lwr-truth,
        upr_centered = upr-truth
      ) %>%
      mutate(sim = sim_)
    out[[sim]] <- tbl1
    setTxtProgressBar(pb, sim)
  }
  close(pb)
  return(do.call("rbind", out))
}
pois_sims <- run_sims(20)
saveRDS(pois_sims, "sims/sim1/pois_sims.rds")
```

```{r}
sim1 <- readRDS("sims/sim1/pois_sims.rds")

# visuals
plot_params <- c(
  # unique(sim1$param[grepl("pd_prob", sim1$param)])
  unique(sim1$param[grepl("alpha", sim1$param)]), unique(sim1$param[grepl("delta", sim1$param)])
)

ggplot() + 
  geom_linerange(
    data = sim1 %>%
      mutate(
        sim = factor(sim)
      ) %>% 
      filter(
        param %in% plot_params
      ),
    aes(
      y = param, x = mean_centered, 
      xmin = lwr_centered, xmax = upr_centered
    ),
    position = position_dodge2(.5),
    alpha = .2
  ) +
  geom_errorbar(
    data = sim1 %>%
      mutate(
        sim = factor(sim)
      ) %>%
      filter(
        param %in% plot_params
      ) %>%
      group_by(param) %>%
      mutate(
        capture = as.numeric(as.character(capture))
      ) %>%
      summarize(
        mean_mean_centered = mean(mean_centered),
        mean_lwr_centered = mean(lwr_centered),
        mean_upr_centered = mean(upr_centered),
        coverage = mean(capture)
      ),
    aes(
      y = param, x = mean_mean_centered,
      xmin = mean_lwr_centered,
      xmax = mean_upr_centered,
      col = coverage
    ),
    width = .5,
    size = 1.1
  ) +
  theme_bw() +
  geom_vline(
    data = sim1 %>%
      mutate(
        sim = factor(sim)
      ) %>% 
      filter(
        param %in% plot_params
      ) %>%
      dplyr::select(param) %>%
      distinct() %>%
      mutate(int = 0), 
    aes(xintercept = int), 
    linetype = "dotdash",
    alpha = .5
  ) +
  scale_color_gradientn(
    limits = c(0,1),
    colors = c("#a1d76a", "#e9a3c9") # PiYG palette
  )
```




## Negative binomial N-mixture model

```{r, eval = T, cache = F}
negbin_code <- nimbleCode({
  # likelihood
  for(site in 1:nsites){
    log(lambda[site]) <- inprod(alpha[1:p_alpha], W[site, 1:p_alpha])
    nbp[site] <- phi / (phi + lambda[site])
    N[site] ~ dnegbin(prob = nbp[site], size = phi)
  }
  for(row in 1:nrows){
    logit(p[row]) <- inprod(delta[1:p_delta], V[row, 1:p_delta])
    y[row] ~ dbinom(prob = p[row], size = N[site_ndx[row]])
  }

  # priors
  for(i in 1:p_alpha){
    alpha[i] ~ dnorm(0, sd = 2)
  }
  for(i in 1:p_delta){
    delta[i] ~ dnorm(0, sd = 2)
  }
  phi ~ T(dnorm(0, 1), 0, Inf)
})
negbin_code
```

### Simulated data

```{r, eval = T, cache = F}
# simulate data
dat <- nmixture_sim(
  seed = 01242023,
  dat = sim1_dfs$mt_covs_grid,
  visit_dat = sim1_dfs$visit_covs,
  family = "negbin",
  zif = FALSE,
  nsites = 75, 
  nvisits = 8
)
```

```{r}
ggplot() +
  geom_sf(
    data = dat$site_df, size = .1, fill = NA
  ) +
  geom_sf(
    data = dat$site_df_obs, size = .1, aes(fill = log(N), col = log(N))
  ) +
  scale_color_gradientn(
    colors = c("#a1d76a", "#e9a3c9") # PiYG palette
  ) + 
  scale_fill_gradientn(
    colors = c("#a1d76a", "#e9a3c9") # PiYG palette
  ) +
  theme_bw()
```

### Fit model

```{r, eval = F}
# fit model
fit <- nimbleMCMC(
  code = negbin_code,
  data = list(
    y = dat$visit_df_obs$y
  ),
  constants = list(
    nsites = nrow(dat$site_df_obs),
    nrows = nrow(dat$visit_df_obs),
    W = dat$obs_design$W,
    V = dat$obs_design$V,
    p_alpha = length(dat$params$alpha),
    p_delta = length(dat$params$delta),
    site_ndx = dat$visit_df_obs$grts_id %>% 
      as.factor %>% as.numeric
  ),
  monitors = c("alpha", "delta", "phi", "N", "p"),
  niter = 20000,
  nburnin = 10000,
  nchains = 3
)
saveRDS(fit, file = "fits/negbin.rds")
```

### Diagnostics

```{r}
fit <- readRDS("fits/negbin.rds")
trace_plot(fit, c("alpha[1]", "alpha[2]", "delta[1]", "delta[2]", "phi"), nrow = 2)
```

### Posterior summaries

```{r}
tmp <- nimble_summary(fit)
tbl1 <- tibble(
  param = rownames(tmp),
  mean = tmp[,1],
  lwr = tmp[,5],
  upr = tmp[,9],
  rhat = tmp[,10],
  neff_bulk = tmp[,11],
  neff_tail = tmp[,12]
) %>%
  mutate(
    truth = c(
      dat$site_df_obs$N,
      dat$params$alpha, dat$params$delta,
      dat$visit_df_obs$p,
      dat$params$phi
    )
  ) %>%
  mutate(
    capture = factor(
      ifelse(truth >= lwr & truth <= upr, 1, 0)
    )
  ) %>%
  mutate(
    mean_centered = mean-truth,
    lwr_centered = lwr-truth,
    upr_centered = upr-truth
  )

tbl1 %>%
  filter(grepl("alpha", param) | grepl("delta", param) | grepl("phi", param)) %>%
  ggplot() +
  geom_pointrange(
    aes(y = param, xmin = lwr_centered, xmax = upr_centered, x = mean_centered, col = capture)
  ) +
  theme_bw() +
  geom_vline(aes(xintercept = 0))

tbl1 %>%
  filter(grepl("N", param)) %>%
  sample_n(15) %>%
  ggplot() +
  geom_pointrange(
    aes(y = param, xmin = lwr_centered, xmax = upr_centered, x = mean_centered, col = capture)
  ) +
  theme_bw() +
  geom_vline(aes(xintercept = 0))

tbl1 %>%
  filter(grepl("p", param)) %>%
  sample_n(20) %>%
  ggplot() +
  geom_pointrange(
    aes(y = param, xmin = lwr_centered, xmax = upr_centered, x = mean_centered, col = capture)
  ) +
  theme_bw() +
  geom_vline(aes(xintercept = 0))
```

### Baby simulation study

Twenty simulated data sets with random generating values. 

```{r, eval = F}
run_sims <- function(nsims){
  out <- list()
  
  pb <- txtProgressBar(min = 0, max = nsims, style = 3, width = 50, char = "=")  
  for(sim in 1:nsims){
    sim_ <- sim
    
    # simulate data
    dat <- nmixture_sim(
      seed = sim,
      dat = sim1_dfs$mt_covs_grid,
      visit_dat = sim1_dfs$visit_covs,
      family = "negbin",
      zif = FALSE,
      nsites = 75, 
      nvisits = 8
    )
    
    # fit model
    fit <- suppressMessages({nimbleMCMC(
      code = negbin_code,
      data = list(
        y = dat$visit_df_obs$y
      ),
      constants = list(
        nsites = nrow(dat$site_df_obs),
        nrows = nrow(dat$visit_df_obs),
        W = dat$obs_design$W,
        V = dat$obs_design$V,
        p_alpha = length(dat$params$alpha),
        p_delta = length(dat$params$delta),
        site_ndx = dat$visit_df_obs$grts_id %>% 
          as.factor %>% as.numeric
      ),
      monitors = c("alpha", "delta", "phi", "N", "p"),
      niter = 10000,
      nburnin = 500,
      nchains = 3,
      progressBar = F
    )})
    
    # summarize
    tmp <- nimble_summary(fit)
    tbl1 <- tibble(
      param = rownames(tmp),
      mean = tmp[,1],
      lwr = tmp[,5],
      upr = tmp[,9],
      rhat = tmp[,10],
      neff_bulk = tmp[,11],
      neff_tail = tmp[,12]
    ) %>%
      mutate(
        truth = c(
          dat$site_df_obs$N,
          dat$params$alpha, dat$params$delta,
          dat$visit_df_obs$p,
          dat$params$phi
        )
      ) %>%
      mutate(
        capture = factor(
          ifelse(truth >= lwr & truth <= upr, 1, 0)
        )
      ) %>%
      mutate(
        mean_centered = mean-truth,
        lwr_centered = lwr-truth,
        upr_centered = upr-truth
      ) %>%
      mutate(sim = sim_)
    out[[sim]] <- tbl1
    setTxtProgressBar(pb, sim)
  }
  close(pb)
  return(do.call("rbind", out))
}
negbin_sims <- run_sims(20)
saveRDS(negbin_sims, "sims/sim1/negbin_sims.rds")
```

```{r}
sim1 <- readRDS("sims/sim1/negbin_sims.rds")

# visuals
plot_params <- c(
  # unique(sim1$param[grepl("pd_prob", sim1$param)])
  unique(sim1$param[grepl("alpha", sim1$param)]), unique(sim1$param[grepl("delta", sim1$param)]), "phi"
)

ggplot() + 
  geom_linerange(
    data = sim1 %>%
      mutate(
        sim = factor(sim)
      ) %>% 
      filter(
        param %in% plot_params
      ),
    aes(
      y = param, x = mean_centered, 
      xmin = lwr_centered, xmax = upr_centered
    ),
    position = position_dodge2(.5),
    alpha = .2
  ) +
  geom_errorbar(
    data = sim1 %>%
      mutate(
        sim = factor(sim)
      ) %>%
      filter(
        param %in% plot_params
      ) %>%
      group_by(param) %>%
      mutate(
        capture = as.numeric(as.character(capture))
      ) %>%
      summarize(
        mean_mean_centered = mean(mean_centered),
        mean_lwr_centered = mean(lwr_centered),
        mean_upr_centered = mean(upr_centered),
        coverage = mean(capture)
      ),
    aes(
      y = param, x = mean_mean_centered,
      xmin = mean_lwr_centered,
      xmax = mean_upr_centered,
      col = coverage
    ),
    width = .5,
    size = 1.1
  ) +
  theme_bw() +
  geom_vline(
    data = sim1 %>%
      mutate(
        sim = factor(sim)
      ) %>% 
      filter(
        param %in% plot_params
      ) %>%
      dplyr::select(param) %>%
      distinct() %>%
      mutate(int = 0), 
    aes(xintercept = int), 
    linetype = "dotdash",
    alpha = .5
  ) +
  scale_color_gradientn(
    limits = c(0,1),
    colors = c("#a1d76a", "#e9a3c9") # PiYG palette
  )
```


